Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Radiant panel data, figures and tex

\dedication{To my wife and family}

@@

The radiant flooring panel test method is known as ASTM~E648, Standard Method of Test for Critical Radiant Flux of Floor-Covering Systems Using a Radiant Heat Energy Source~\cite{ASTM_E648}. A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel. The panel is inclined at 30~$^{\circ}$, providing a heat flux on the test specimen varying from 10~kW/m$^2$ at the point closest to the panel to 1~kW/m$^2$ at the farthest point. A pilot flame is used to ignite the test sample. The objective of the test is to determine the critical radiant flux for a given sample.  The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped. For this study the samples examined were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.

@@

@@

@@

\bibliography{../References/Madrzykowski_Thesis,../../../Bibliography/FDS_refs}
\end{document}

>>>>

\dedication{To my wife and family}  work family

@@

The radiant flooring panel test method is known as ASTM~E648, Standard Method of Test for Critical Radiant Flux of Floor-Covering Systems Using a Radiant Heat Energy Source~\cite{ASTM_E648}. A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel. The panel is inclined at 30~$^{\circ}$, and under standard operating conditions provide a heat flux on the test specimen varying from 10~kW/m$^2$ at the point closest to the panel to 1~kW/m$^2$ at the farthest point. For these experiments a higher heat flux profile was required, so the gas air increased    comback   to  Figure~\ref{FRP_HF_Calibration}

A pilot flame is used to ignite the test sample. The objective of the test is to determine the critical radiant flux for a given sample.  The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped. For this study the samples examined were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.

\begin{figure}[p]
	\centering
	\includegraphics[width=\textwidth]{../Figures/FRP_HF_Calibration} \\
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
	\label{FRP_HF_Calibration}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.  ]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.  Each row of samples represents three replicate experiments at a given heat flux for 600s. Begining with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.  }
	\label{RP_GB_Front}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=\textwidth]{../Figures/RPGB_SET} \\
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.  ]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.  Each row of samples represents three replicate experiments at a given heat flux for 600s. Begining with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.  }
	\label{RPGB_SET}
\end{figure}

@@

\bibliography{../References/Madrzykowski_Thesis}
\end{document}
